
\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{multicol}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Mueez}{Aizaz}
{ 
{Rütscher Str. 121, 52072, Aachen Germany} \\
{mueez.aizaz23@gmail.com} | +49 179 4195248
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{RWTH Aachen}

\descript{M.Sc Biomedical Engineering}
\location{2013 –  | Germany}

\sectionspace % Some whitespace after the section

\subsection{NUST Islamabad}
\descript{B.E Computer Systems Engineering}
\location{2007 – 2011 | Pakistan}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Saint Mary's Academy}

\location{May 2007 | Rawalpindi, Pakistan}
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Anatomy \\
Physiology \\
Bio and Fluid Mechanics \\
Game Theory \\
Medical Imaging \\
Image Processing \\
Systems Biology \\
Cell Culture and Tissue Engineering \\
Material Science and Processing \\
Project Management \\

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Undergraduate}


Computer System Architecture \\
Microprocessor Based Design \\
Linear Signal and Systems \\
Operating Systems \\
Digital Image Processing \\
Digital Signal Processing \\
Digital Communication \\
Communication Networks \\
Digital System Design \\
Control Systems \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

%\location{Over 5000 lines:}
C \textbullet{} C++ \textbullet{} Matlab \textbullet{} R \\ Network Fundamentals
%\location{Over 1000 lines:}
%Shell \textbullet{} JavaScript \textbullet{} Python \textbullet{} \LaTeX\ \\ 
%HTML5 \textbullet{} CSS \textbullet{} PHP 

\location{Familiar:}
Latex \textbullet{} MySQL \\ 


\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------
%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the 

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{AICES}
\descript{| Student Job }

\location{May 2014 – Mar 2015 | Aachen, Germany}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item High Throughput Sequencing Data.
\item MusMusculus genomic data compared with RNA in R.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{Elixir Technologies}
\descript{| Quality Assurance Engineer}

\location{Nov 2012 – Aug 2013 | Islamabad, Pakistan}
\begin{tightitemize}
\item Provide Technical Assistance to companies using softwares Opus and Design Pro Tools,
both of which were developed at Elixir Technologies
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Nayatel Pvt. Ltd.}
\descript{| Operations Engineer}

\location{Mar 2012 – Aug 2012 | Islamabad, Pakistan.}
\begin{tightitemize}
\item Nayatel is private Internet Service Provider specialising in optic fibres.
\item Worked in the Technical Assistance Centre providing remote assistace to customers
regarding network connectivity issues.
\end{tightitemize}

\sectionspace % Some whitespace after the section
\section{Projects}
\runsubsection{Energy Consumption Optimization in HVAC Systems}
\descript{| Bachelors Degree Project}

\location{Feb 2011 – May 2011 | Islamabad, Pakistan}
\begin{tightitemize}
\item Energy Consumption Optimization of an air conditioner using ODE to represent the air
flow model of the room and sensors to control the air conditioner.
\item A device was developed which would sense temperatures at specific area in a room and with integration with the AC remote turn it off when desired temperature is achieved and turn it back on again as the temperature rose.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Optical Digit Recognition}
\descript{}

\location{Mar 2010 – Jun 2010 | Islamabad, Pakistan}
\begin{tightitemize}
\item Using Neural Networks a system was setup that was able to recognize hand written digits and output in digital form.
\item The neural network was setup using the neural network toolbox in Matlab.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\begin{multicols}{2}
\section{About Me}   
\location{DoB}
23/03/1989 \\
\location{Gender}
Male \\
\location{Nationality}
Pakistan \\
\location{Languages}
\textbullet{} English \\
\textbullet{} German  (B1) \\
\textbullet{} Urdu \\

\columnbreak

\section{Extra curricular} 
Hello, here is some text without a meaning.  This text should show what a printed text will look like at this place.
If you read this text, you will get no information.  Really?  Is there no information?  Is there.

\end{multicols}


\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\end{document}